Blame and Coercion: Together Again for the Second Time

### 2019-10-17 paper.tex
define observe(v) = o
remove bisimilarity

Let $ o $ range over observations. They are what would be observed if a 
program terminates. Observations include all value constructors and blame.

@@

We use bisimulation to proof equivalence between the two machines.
\todo[inline]{Which two machines? -JS}
The state bisimilarity ($\eqvDS{C}{s}{s}$) is mostly derived from the 
definitions of $ \mathcal{D} $. Exceptions include the bisimilarity relations 
between continuations, between values, and from continuations to 
pre-continuations. We omit subscripts when there is no ambiguity.

@@

With the properties of surely \lazyD{} cast representation, it is 
straightforward to proof that 
all machines instantiated with these cast representations bisimulate each 
other. 
The state bisimilarity ($\eqvS{C}{C}{s}{s}$) is 
derived from the definition of states.
\todo[inline]{The term ``bisimilarity'' has a different technical meaning from
	``bisimulation relation''. I don't think you are using it properly
	in the above sentence. -JS}
We omit subscripts when there is no 
ambiguity. \begin{gather*}
\inference{
	\rho_1 \approx \rho_2 &
	\kappa_1 \approx \kappa_2
}{
	\sOOinspect{e}{\rho_1}{\kappa_1} \approx \sOOinspect{e}{\rho_2}{\kappa_2}
}
\quad
\inference{
	\kappa_1 \approx \kappa_2 &
	v_1 \approx v_2
}{
	\sOOreturn{v_1}{\kappa_1} \approx \sOOreturn{v_2}{\kappa_2}
}
\quad
\inference{
}{
	\sOOhalt{o} \approx \sOOhalt{o}
}
\end{gather*}

>>>>

Let $ o $ range over observations. They are what would be observed if a 
program terminates. Observations include all value constructors and blame.
The function converting values to observations ($ observe(v) = o $) is defined 
in the natural way.

@@

We use bisimulation to proof equivalence between the two machines.
\todo[inline]{Which two machines? -JS}
The bisimulation relation of states ($\eqvDS{C}{s}{s}$) is mostly derived from 
the definitions of $ \mathcal{D} $. Exceptions include the relations 
between continuations, between values, and from continuations to 
pre-continuations. We omit subscripts when there is no ambiguity.

@@

With the properties of surely \lazyD{} cast representation, it is 
straightforward to proof that 
all machines instantiated with these cast representations bisimulate each 
other. 
The bisimulation relation of states ($\eqvS{C}{C}{s}{s}$) is 
derived from the definition of states.
\todo[inline]{The term ``bisimilarity'' has a different technical meaning from
	``bisimulation relation''. I don't think you are using it properly
	in the above sentence. -JS
\\---\\
Fixed.
I learn that $ s_1 \sim s_1 $ reads ``$ s_1 $ is bisimilar to $ s_2 $'' from 
wikipedia. (https://en.wikipedia.org/wiki/Bisimulation).
-KC}
We omit subscripts when there is no 
ambiguity. \begin{gather*}
\inference{
	\rho_1 \approx \rho_2 &
	\kappa_1 \approx \kappa_2
}{
	\sOOinspect{e}{\rho_1}{\kappa_1} \approx \sOOinspect{e}{\rho_2}{\kappa_2}
}
\quad
\inference{
	\kappa_1 \approx \kappa_2 &
	v_1 \approx v_2
}{
	\sOOreturn{v_1}{\kappa_1} \approx \sOOreturn{v_2}{\kappa_2}
}
\quad
\inference{
}{
	\sOOhalt{o} \approx \sOOhalt{o}
}
\end{gather*}
